---
title: "codeBuildR"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description

This package contains useful functions for working with ICD Codes (diagnoses and
procedures), CCS groupings along with NDC drug codes. It also contains datasets used to generate common code groups such as index diseases (e.g., AMI or CDI), 
medications (e.g., antibiotics). 

This package is intended to replace and expand upon the `icdplus` package. All
prior functions and datasets contained in `icdplus` have been placed in this package.

### Structure

Code used to generate common disease, medication or procedure groupings are 
located in `R/disease_codes`, `R/drug_codes` or `R/proc_codes`, respectively. 
These scripts should generate .csv files that reside in `inst/extdata`. Note: 
these files will be stored externally to the package and are saved as raw text
files to manage code revisions on GitHub, but will be installed with the package.

If code used to generate the common disease, medication and procedure groupings
require manually created raw csv files, these should be stored in `data-raw/disease_codes`, `data-raw/drug_codes` or `data-raw/proc_codes`, respectively.


## Examples - Exisiting `icdplus` codes

```{r, message = FALSE}
library(codeBuildr)
```


#### Crosswalk ICD-9-CM and ICD-10-CM codes

Covert ICD-9 code for C.diff to ICD-10
```{r}
icd9_to_icd10("00845")
```

Use `children()` from `icd` package to collect any nested codes
```{r}
icd9_to_icd10("00845") %>% children()
```

Convert ICD-10 back to ICD-9 for C.diff
```{r}
icd10_to_icd9("A047")
```

#### Working with CCS codes

Find a ccs code from a term:
```{r}
find_ccs("flu")
find_ccs("influenza")
```

Get descriptions for CCS codes:
```{r}
explain_ccs(c(1,100))
```

Get ICD-9 codes for a CCS group
```{r}
get_icd_from_ccs(100)
```

Get ICD-10 codes for a CCS group
```{r}
get_icd_from_ccs(100,icd_version = 10)
```


## Examples - Loading Code Sets

#### Loading diagnosis code sets

See the available disease code sets
```{r}
avail_disease_codes()
```

Load disease codes sets
```{r}
load_disease_codes(c("ami","cdi"))
```


#### Loading RX (medication) code sets

See the available rx code sets
```{r}
avail_rx_codes()
```

Load an rx code set
```{r}
all_abx <- load_rx_codes("all_abx")

names(all_abx)

head(all_abx$clindamycin)
```
